---
title       : BMI Calculator
subtitle    : 
author      : Emma
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## First World Problem
  
One of the biggest first world problems is obesitas.  
The massive amounts of junk food and artifical food make us fat. But how fat does it make us?  
    
For this I developed a widget that calculates your Body Mass Index, or BMI.  
Through this BMI you can see if you have a normal weight or have obesitas.

--- 

## BMI Calculator
  
First of all you fill in your weight in kg and your length in cm.  
  
Then you click submit and the calculator will calculate your BMI and give the lower and upper bound of the normal weight category.  
  
    
BMI lower than 18.5 : Underweight  
BMI 18.5-25 : Normal weight  
BMI 25-30 : Overweight  
BMI above 30 : Obesitas  

--- 

## BMI Function
  
The app performs a simple calculation based on the submitted length in cm and weight in kg:
$$BMI= \frac{weightkg}{(lengthcm / 100) * (lengthcm / 100)}$$
  
  
Besides calculating the BMI based on the inputs, the weight interval for normal weight is also calculated. A BMI between 18.5 and 25 is considered normal weight.  
  
The calculator calculates the weights for these BMI's for the submitted length in cm:
$$weightkg= 18.5 * (lengthcm / 100) * (lengthcm / 100)$$
$$weightkg= 25 * (lengthcm / 100) * (lengthcm / 100)$$

--- 

## Example
You fill in a length of 165 cm and a weight of 75 kg.  
The app will run the followeing formulas
```{r}
weightkg <-75
lengthcm<-165
BMI  <- weightkg/((lengthcm / 100) * (lengthcm / 100))
weight_kg_low <- 18.5 * (lengthcm / 100) * (lengthcm / 100)
weight_kg_up <- 25 * (lengthcm / 100) * (lengthcm / 100)
```

---

## Results

```{r}
BMI 
weight_kg_low 
weight_kg_up
```